Software Citation Principles

### 2016-07-24 sc-principles/software-citation-principles.tex
accepting change in intro, removing sentence that Kyle questioned in 6

\niemnote{Do we want a better introduction, to help with the structure of the paper?}
\katznote{We need to keep this short, I think.  I'm not sure what else we can easily do.}
\niemnote{How is this?}

@@

Some software which is, or could be, captured as part of data provenance may not be cited.
Citation is partly a record of software important to a research outcome\footnote{Citation
can be used for many purposes, including for software: which software has been used in
the work, which software has influenced the work, which software is the work superseding,
which software is the work disproving, etc.}, where provenance is a record of all steps
(including software) used to generated particular data within the research process.
Research results, including data, increasingly depend on software~\cite{Hannay:2009wp},
and thus may depend on the specific version
used~\cite{Sandve:2013gh,Wilson:2014aa}. Furthermore, errors in software or
environment variations can affect results~\cite{Morin:2012hz,Soergel:2015aa}.
This implies that for a data research product, provenance data will include some of
the cited software.
Similarly, the software metadata that is recorded as part of data provenance should be
will overlap the metadata recorded as part of software citation for the software that
was used in the work. The data recorded for reproducibility should also overlap
the metadata recorded as part of software citation.
These statements may also be true for software products.
In general, we intend the software citation principles to cover the minimum of what is
necessary for software citation for the purpose of software identification.
Some use cases related to citation (e.g., provenance, reproducibility) might have additional requirements beyond the basic metadata needed for citation, as Table~\ref{tab:use_cases} shows.
%\ssnote{from the data side, an example might be found in the National Climate Assessment (NASA, GCIS) where this is captured in PROV instead?}
%\dmnote{ Mention that the principles are covering what's necessary, not necessarily what is sufficient for a given use case. So perhaps we should discuss things like configurations or bugs? }

>>>>

%\niemnote{Do we want a better introduction, to help with the structure of the paper?}
%\katznote{We need to keep this short, I think.  I'm not sure what else we can easily do.}
%\niemnote{How is this?} \katznote{good}

@@

Some software which is, or could be, captured as part of data provenance may not be cited.
Citation is partly a record of software important to a research outcome\footnote{Citation
can be used for many purposes, including for software: which software has been used in
the work, which software has influenced the work, which software is the work superseding,
which software is the work disproving, etc.}, where provenance is a record of all steps
(including software) used to generated particular data within the research process.
Research results, including data, increasingly depend on software~\cite{Hannay:2009wp},
and thus may depend on the specific version
used~\cite{Sandve:2013gh,Wilson:2014aa}. Furthermore, errors in software or
environment variations can affect results~\cite{Morin:2012hz,Soergel:2015aa}.
This implies that for a data research product, provenance data will include some of
the cited software.
Similarly, the software metadata recorded as part of data provenance will
overlap the metadata recorded as part of software citation for the software that
was used in the work. The data recorded for reproducibility should also overlap
the metadata recorded as part of software citation.
In general, we intend the software citation principles to cover the minimum of what is
necessary for software citation for the purpose of software identification.
Some use cases related to citation (e.g., provenance, reproducibility) might have additional requirements beyond the basic metadata needed for citation, as Table~\ref{tab:use_cases} shows.
%\ssnote{from the data side, an example might be found in the National Climate Assessment (NASA, GCIS) where this is captured in PROV instead?}
%\dmnote{ Mention that the principles are covering what's necessary, not necessarily what is sufficient for a given use case. So perhaps we should discuss things like configurations or bugs? }
